An active sampling model of mental rotation

### 2014-01-21 man/cogsci-2014/cogsci-2014.tex
Add figures to paper

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb}

@@

@@

@@

The experiment consisted of one block of 10 practice trials followed
by two blocks of 100 experiment trials. Within a block, trials were
presented in a random order.

All participants saw the same 10 practice trials as described
above. Participants in different conditions saw different experimental
trials, however. Across participants, there were a total of 800
experimental stimuli (20 shapes $\times$ 20 angles $\times$ 2
same/flipped). These stimuli were split across conditions in the
following manner. First, stimuli were split into four blocks of 200
trials. Within each block, each shape was repeated 10 times and each
rotation was repeated 10 times (5 same, 5 flipped), such that across
all blocks, each stimulus appeared exactly once. Each block was then
split in half. Each participant then completed two half-blocks (not
necessarily both from the original full block).

@@

@@

While there was no time limit on response time, participants were
urged to repond as quickly as possible while still being
accurate. Specifically, we asked them to aim for at least 85\% correct
in the experimental blocks, and provided a score counter to keep them
informed of their accuracy.

@@

>>>>

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{subfig}

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/model-traces.pdf}
    \caption{\textbf{Model traces.}}
    \label{fig:model-traces}
  \end{center}
\end{figure*}

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/response-times.pdf}
    \caption{\textbf{Response times.}}
    \label{fig:response-times}
  \end{center}
\end{figure*}

@@

The experiment consisted 210 total trials: of one block of 10 practice
trials followed by two blocks of 100 experiment trials. Within a
block, trials were presented in a random order.

All participants saw the same 10 practice trials (as described
above). There were a total of 800 experimental stimuli (20 shapes
$\times$ 20 angles $\times$ 2 same/flipped), which were split into 8
blocks of 100 across conditions in the following manenr. First,
stimuli were split into four blocks of 200 trials. Within each block,
each shape was repeated 10 times and each rotation was repeated 10
times (5 same, 5 flipped), such that across all blocks, each stimulus
appeared exactly once. Each block was then split in half. Each
participant then completed two half-blocks (not necessarily both from
the original full block).

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=0.85\textwidth]{../../figures/D/accuracy.pdf}
    \caption{\textbf{Accuracy.}}
    \label{fig:response-times}
  \end{center}
\end{figure*}

@@

While there was no limit on response time, participants were urged to
repond as quickly as possible while still being
accurate. Specifically, we asked them to aim for at least 85\%
accuracy in the experimental blocks, and provided a counter to keep
them informed of their score.

@@

\begin{figure}[t]
  \centering
  \subfloat{\includegraphics[width=0.25\textwidth]{../../figures/D/trial-vs-accuracy.pdf}}%
  \subfloat{\includegraphics[width=0.25\textwidth]{../../figures/D/trial-vs-time.pdf}}
  \caption{\textbf{Effect of learning.}}
  \label{fig:learning}
\end{figure}

response time as a function of rotation

accuracy as a function of rotation

practice effects
